Exponential family measurement error models for single-cell CRISPR screens

### 2023-07-27 presentation/glmeiv_talk.tex
start text outline
update sim spec object for experiment 0 to be compatible with new simulatr

\begin{frame}
\frametitle{(1) The perturbation is unobserved, and (2) technical factors are present.}
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{../figures/fig1/dag}
	\label{dag}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{(3) Unperturbed cells exhibit background gRNA reads.}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../figures/fig1/density_plot_annotated.png}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{(4) The count data are highly discrete.}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../figures/fig1/mRNA_count_hist_annotated.png}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Problem 1: There is no clear location in the data at which to draw the threshold.}
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{../figures/fig2/histograms}
\end{figure}

@@

\begin{frame}
\frametitle{The thresholding method shows clear attenuation bias.}
\begin{itemize}
\item We set $\beta_m$ to 1.
\end{itemize}

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../figures/fig2/att_bias}
\end{figure}

@@

\begin{frame}
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{../figures/fig3/simulation_warmup_arm_g}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Estimates and CIs produced by GLM-EIV and the thresholding method were similar.}
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{../figures/fig5/comparison}
\end{figure}
\begin{center}
Candidate \textit{cis} pairs in Xie et al.\ data.
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{Thank you.}
Acknowledgments:
\begin{itemize}
\item Xuran Wang helped with the Xie data preprocessing.
\item All analyses were run on Pittsburgh Supercomputer.
\end{itemize}
\end{frame}

>>>>

% \begin{frame}
% \frametitle{(1) The perturbation is unobserved, and (2) technical factors are present.}
% \begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{../figures/fig1/dag}
%	\label{dag}
%\end{figure}
% \end{frame}

%\begin{frame}
%\frametitle{(3) Unperturbed cells exhibit background gRNA reads.}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.75\linewidth]{../figures/fig1/density_plot_annotated.png}
%\end{figure}
% \end{frame}

% \begin{frame}
%  \frametitle{(4) The count data are highly discrete.}
% \begin{figure}
%	\centering
%	\includegraphics[width=0.75\linewidth]{../figures/fig1/mRNA_count_hist_annotated.png}
% \end{figure}
% \end{frame}

@@

%\begin{frame}
%\frametitle{Problem 1: There is no clear location in the data at which to draw the threshold.}
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{../figures/fig2/histograms}
%\end{figure}
%\end{frame}

@@

%\begin{frame}
%\frametitle{The thresholding method shows clear attenuation bias.}
%\begin{itemize}
%\item We set $\beta_m$ to 1.
%\end{itemize}

%\begin{figure}
%	\centering
%	\includegraphics[width=0.75\linewidth]{../figures/fig2/att_bias}
%\end{figure}
%\end{frame}

@@

%\begin{frame}
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{../figures/fig3/simulation_warmup_arm_g}
%\end{figure}
%\end{frame}

@@

%\begin{frame}
%\frametitle{Estimates and CIs produced by GLM-EIV and the thresholding method were similar.}
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{../figures/fig5/comparison}
%\end{figure}
%\begin{center}
%Candidate \textit{cis} pairs in Xie et al.\ data.
%\end{center}
%\end{frame}

@@

\begin{frame}
\frametitle{Thank you.}
Acknowledgments:
\begin{itemize}
\item Thanks to Xuran Wang for helping with the Xie data preprocessing.
\item All analyses were run on Pittsburgh Supercomputer.
\end{itemize}
\end{frame}

### 2023-07-27 presentation/glmeiv_talk_updated.tex
update sim spec object for experiment 0 to be compatible with new simulatr

\documentclass{beamer}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{/Users/timbarry/optionFiles/mymacros}
%Information to be included in the title page:
\title{A generalized errors-in-variables model, with application to single-cell CRISPR screens}
\author{Tim Barry$^1$, Eugene Katsevich$^2$, Kathyrn Roeder$^1$}
\institute{$^1$CMU Statistics and Data Science\\ $^2$Wharton Statistics and Data Science}
\date{September 2021}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\bibliography{/Users/timbarry/optionFiles/glmeiv.bib}
\bibliographystyle{apalike}

>>>>

\documentclass{beamer}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{/Users/timbarry/optionFiles/mymacros}
%Information to be included in the title page:
\title{Exponential family measurement error models for single-cell CRISPR screens}
\author{Timothy Barry$^1$, Eugene Katsevich$^2$, Kathyrn Roeder$^1$}
\institute{$^1$CMU Statistics and Data Science\\ $^2$Wharton Statistics and Data Science}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\bibliography{glmeiv.bib}
\bibliographystyle{apalike}
